\begin{thebibliography}{24}
\bibitem{soryuushi}
南部陽一郎・木下東一郎・牧二郎・中西襄・政池明,
”大学院 素粒子物理学１ 素粒子の基本的性質”
講談社サイエンティフィック
\bibitem{oku}
奥山広貴, ”HL-LHC ATLAS ピクセル検出器量産時の品質試験に向けた データベースシステムの構築”,
\url{https://cernbox.cern.ch/index.php/s/IBO6BptySxPwD6L}, 東京工業大学大学院修士論文 (2021)
\bibitem{kubotan}
窪田ありさ, ”HL-LHC ATLAS 実験用新型ピクセル検出器の系統評価と 量産時に向けた試験管理システムの開発”,
\url{https://cernbox.cern.ch/index.php/s/BdhvSTAuuE5xHXt}, 東京工業大学大学院修士論文 (2020)
\bibitem{kimu}
Eunchong Kim, ”Development of DAQ test system and database for the HL-LHC ATLAS production Pixel detector",
\url{https://cernbox.cern.ch/index.php/s/ZyYwYnMxeCSoeZl}, 東京工業大学大学院修士論文(2019)
\bibitem{LHC}
The CERN accelerator complex, ”The CERN accelerator complex”, \url{https://cds.cern.ch/images/OPEN-PHO-ACCEL-2013-056-1}, CERN Document Server (最終更新: 2018年7月)
\bibitem{ATLAS}
Computer generated image of the whole ATLAS detector, "Computer generated image of the whole ATLAS detector", \url{https://cds.cern.ch/record/1095924}, CERN Document Server (最終更新: 2015年2月).
\bibitem{studyofID}
The ATLAS Collaboration, "Study of the material of the ATLAS inner detector for Run 2 of the LHC"(2017), \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/PAPERS/PERF-2015-07/}
\bibitem{calocalo}
Computer Generated image of the ATLAS calorimeter, "Computer Generated image of the ATLAS calorimeter", \url{https://cds.cern.ch/images/CERN-GE-0803015-01}, CERN Document Server (最終更新: 2018年6月).
\bibitem{hl-lhc}
CERN Accelerating science, “The HL-LHC project”, 2021年12月閲覧,
\url{https://hilumilhc.web.cern.ch/content/hl-lhc-project}
\bibitem{lhc-lumi}
Burkhard Schmidt, "The High-Luminosity upgrade of the LHC: Physics and Technology Challenges for the Accelerator and the Experiments" (2015),
\url{https://iopscience.iop.org/article/10.1088/1742-6596/706/2/022002/pdf}
\bibitem{crab}
細山 謙二, "超伝導クラブ空洞" (2008), \url{https://www.jstage.jst.go.jp/article/jcsj/43/4/43_4_132/_pdf}
\bibitem{itk}
The ATLAS Collaboration, "ATLAS Inner Tracker Pixel Detector Technical Design Report" (2018), \url{https://cds.cern.ch/record/2285585/files/ATLAS-TDR-030.pdf}
\bibitem{higgs}
The ATLAS Collaboration. “Combined measurements of Higgs boson production and decay using up to $80$ fb$^{-1}$ of proton–proton collision data at $\sqrt{s}=13$ TeV collected with the ATLAS experiment” (2018). CERN Document Server. \url{http://cdsweb.cern.ch/record/2629412/}
%\bibitem{kek}
%\url{https://atlas.kek.jp/main/movie/photos/physics/index.html}
%\bibitem{darkmatter}
%\url{https://home.cern/science/physics/dark-matter}
\bibitem{bethe}
Particle Data Group, 33. Passage of particles through matter 1,
\url{https://pdg.lbl.gov/2019/reviews/rpp2018-rev-passage-particles-matter.pdf}
\bibitem{typeinversion}
M. Moll, “Displacement Damage in Silicon Detectors for High Energy Physics”, IEEE Transactions on Nuclear Science, Aug. 2018. DOI: 10. 1109/TNS.2018.2819506.
\bibitem{timewalk}
Beniamino Di Girolamo, "The ATLAS Pixel Detector" (2011), \url{https://pos.sissa.it/137/006/pdf}
\bibitem{rd53a}
Garcia-Sciveres, Maurice, “The RD53A Integrated Circuit” (2019), \url{https://cds.cern.ch/record/2287593}, CERN Document Server, Modified Sep 2019.
\bibitem{calibsoft}
Maria Elena Stramaglia, "Calibration analysis software for the ATLAS Pixel Detector" (2015), \url{https://cds.cern.ch/record/2027805/files/ATL-INDET-PROC-2015-003.pdf}
\bibitem{pixeldb}
M. Verducci, "ATLAS conditions database experience with the LCG COOL conditions database project" (2008),
\url{https://iopscience.iop.org/article/10.1088/1742-6596/119/4/042031}
\bibitem{tothennka}
ATLAS physics plots, \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/PLOTS/PIX-2018-009/fig_05.png}, 2021年12月閲覧
\bibitem{pixeltypes}
Daniel Adam Dobos, "Production accompanying testing of the ATLAS Pixel module" (2017),
\url{https://cds.cern.ch/record/1016933/files/thesis-2007-016.pdf}
\bibitem{lingxin}
Lingxin Meng, "RD53A Module Testing Document" (最終更新: 2021年9月), \\
\url{https://cds.cern.ch/record/2702738/files/ATL-COM-ITK-2019-045.pdf}
\bibitem{electricaldoc}
Massimiliano Antonello, "Digital module electrical testing" (2020), \\
\url{https://cds.cern.ch/record/2723333/files/ATL-COM-ITK-2020-020.pdf}
\bibitem{sldo}
Vasilije Perovic, CMS Tracker Group. “Serial powering in four-chip prototype RD53A modules for Phase 2 upgrade of the CMS pixel detector”. ScienceDirect. 2020-10. \url{https://www.sciencedirect.com/science/article/pii/S0168900220308330}
\bibitem{mongo}
MongoDB, "MongoDB Documentation", \url{https://docs.mongodb.com}, 2021年12月閲覧
\bibitem{human}
Neville W. Sachs, P.E., "Practical Plant Failure Analysis" (2019), Economics, Finance, Business \& Industry, Engineering \& Technology
\end{thebibliography}
